%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Teodor \DJ{}urić} \\ \vspace{1pt}
    \small \href{mailto:djuric.teodor25@gmail.com}{\underline{djuric.teodor25@gmail.com}} $|$
    \href{https://www.linkedin.com/in/teodor-%C4%91uri%C4%87-008a28229/}{\underline{linkedin.com/in/teodor-\dj{}urić-008a28229}}
    $|$
    \href{https://github.com/teodord25}{\underline{github.com/teodord25}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Technical Sciences}{Novi Sad, Serbia}
      {Bachelor's in Software Engineering and Information Technologies}{Jul. 2021 -- Present}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


\resumeSubheading
  {Software Engineer}{Jul 2023 -- Dec 2024}
  {Soft-tronic}{Senta (Remote from Novi Sad)}
  \resumeItemListStart

    \resumeItem{
      \textbf{Architected and implemented SmartServe, a full-stack SSR framework,} leveraging inversion of control 
      and dependency injection to ensure a modular, maintainable codebase.
    }

    \resumeItem{\textbf{Collaborated} on various PHP projects, contributing code and assisting with development tasks.}

    \resumeItem{\textbf{Mentored} interns in coding skills and best practices, fostering a culture of knowledge sharing.}

    \resumeItem{\textbf{Spearheaded} the adoption of Git and GitHub within the company by pitching, preparing, and then delivering a presentation to the entire company on the benefits and usage of Git and GitHub.}

    \resumeItem{\textbf{Created scripts} using Python to scrape the client's old website for photos and information, and utilized the WordPress API to automate the creation of posts, significantly reducing manual data transfer efforts.}

    \resumeItem{\textbf{Automated} the process of loading smartcard information into web forms on a website using C++ and a government API coupled with a minimal local server to serve generated JSON data to the website.}

    \resumeItem{\textbf{Optimized} and cleaned up poorly designed and neglected databases.}

    \resumeItem{\textbf{Proactively addressed infrastructure needs} by taking on DevOps responsibilities.}
    \resumeItemListStart
      \resumeItem{\textbf{Dockerized existing projects} supporting hundreds of heat pumps (bes.rs) consisting of microcontroller backends, app backends (BES Heat Pump Controller) and the administrative webpage.}
      \resumeItem{\textbf{Configured and maintained} the physical servers hosting the BES partner's software solutions.}
      \resumeItem{\textbf{Developed GitHub Actions workflows} that automatically deploy updates to servers over SSH upon detecting new tags, significantly reducing manual deployment efforts and minimizing downtime.}
    \resumeItemListEnd


  \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Selected Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{SmartServe} $|$ \emph{Go, Echo, Docker, MySQL, GORM, Git, GitHub Actions}}{Feb 2024 -- Dec 2024}
        \resumeItemListStart

          \resumeItem{
            \textbf{Designed a flexible, decoupled architecture} that allowed component reuse across multiple projects, demonstrating the framework’s scalability and flexibility. (e.g., SmartServe-Table, SmartServe-Hotel)
          }

          \resumeItem{\textbf{Developed SmartServe-Core}, a central library providing essential functionalities.}
          \resumeItem{\textbf{Implemented inversion of control} by using dependency injection and defining clear interfaces, enabling the framework to manage application flow and enhance extensibility.}
          \resumeItem{\textbf{Optimized performance and scalability} by continuously reducing complexity where it isn't needed.}
          \resumeItem{\textbf{Automated testing and deployment} using GitHub Actions, ensuring code quality and streamlining CI/CD.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{SmartServe-Table (Food Plaza)} $|$ \emph{Go, SmartServe, Templ (Go), HTMX, JavaScript, HTML/CSS}}{May 2024 -- Dec 2024}
        \resumeItemListStart
          \resumeItem{\textbf{Developed a full-stack web application} for restaurant management using the SmartServe framework.}
          \resumeItem{\textbf{Engineered dynamic, responsive user interfaces} using HTMX reducing reliance on complex JavaScript.}
          \resumeItem{\textbf{Integrated QR code functionality} to enable seamless table ordering, enhancing customer experience.}
          \resumeItem{\textbf{Conducted end-to-end testing} with Selenium and Nix shell to ensure reliability and robustness.}
        \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Nebula} $|$ \emph{Rust} }{{\small\href{https://github.com/drag0dev/nebula}{\underline{github.com/drag0dev/nebula}}}  Jul 2023 -- Sep 2023}
        \resumeItemListStart
        \resumeItem{\textbf{Co-developed a key-value NoSQL database} in Rust for a university project, demonstrating adaptability and the ability to quickly learn and apply new programming paradigms.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Additional Projects} $|$ \href{https://github.com/teodord25}{github.com/teodord25}}{}{}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, Rust, JavaScript, PHP, HTML/CSS, Bash, Java, C\#, C++, Nushell, SQL, Lua, Nix} \\
     \textbf{Frameworks}{: SmartServe (in-house custom), Echo (Go), Angular, WordPress} \\
     \textbf{Developer Tools}{: Neovim/Vim/Vi, Docker, SSH, TMUX, Git, Github Actions, Nix Shell, VS Code, Visual Studio} \\
     \textbf{Libraries}{: HTMX, Templ, React, GORM} \\
     \textbf{Technologies}{: Linux, MySQL, PostgreSQL, NixOS, Nix, LaTeX} \\
     \textbf{Natural Languages}{: Serbian (native), English (fluent), Hungarian (fluent)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
